Supplementary Information

### 2020-11-16 doc/manuscript/MEE_manuscript_SI.Rmd
replace mock figure with real comparison to traditional approach

\newpage 
## Figure S1. Comparison of our approach with traditional methods of identifying climate signals
![**Figure S1 | (Comparison of traditional approaches with ours).**  (THIS FIGURE IS JUST A MOCK-UP --NOT REAL DATA. REAL FIGURE WILL INCLUDE 3-4 COMMONLY STUDIED SPECIES FROM DIFFERENT SITES.) ](tables_figures/SI_figures/mock_comparison_traditional_method.png){ width=70% }

>>>>

\newpage 
## Figure S1. Comparison of our approach with traditional methods of identifying climate signals

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_CedarBreaks_PSME_pre.png){ width=70% }

![](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_CedarBreaks_PSME_tmx.png){ width=70% }

**Figure S1 | (Comparison of traditional approaches with ours).**  (Example is Cedar Breaks PSME response to (a) PRE and (b) TMX. We have 3 more sites...)
